Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-10-27 cape.Rnw
merge Social class and exposure to one slide
merge Social class and exposure to split slide

@@

\begin{frame}{\sc Social class}

\begin{enumerate}
\item \emp{\tt elite}, HISCLASS 1 and 2. Higher managers and professionals.
\item \emp{\tt middle}, HISCLASS 3, 4, 5, 6, and 8. Lower managers, lower white collar, and farmers.
%%\item \emp{\tt lowWhiteC}, HISCLASS 4, 5 and 6. Lower white collar.
\item \emp{\tt worker}, HISCLASS 7, 9, 10, 11 and 12. Workers of different skills including farm workers.
\end{enumerate}

@@

@@

\includegraphics[height=5cm]{myfigs/Top_incomes}
\end{center}

@@

>>>>

\newcommand{\empg}[1]{\textcolor{green}{#1}}

\newcommand{\empr}[1]{\textcolor{red}{#1}}

@@

\begin{frame}{Social class and relative exposure}

\begin{center}
\small {Women \hspace{4cm} Men}
\includegraphics[height = 3cm]{figs/art2-hiscskumw-1}
\includegraphics[height = 3cm]{figs/art2-hiscskumm-1}
\end{center}
\footnotesize
\begin{description}
\item[\bf \textcolor{black}{elite}] {\sc Hisclass} 1 and 2. \emph{Higher managers and professionals.}
\item[\empg{\bf middle}] {\sc Hisclass} \empg{3, 4, 5, 6, and 8}. \emph{Lower managers, lower white collar, and farmers.}
%%\item \emp{\tt lowWhiteC}, HISCLASS 4, 5 and 6. Lower white collar.
\item[\emp{\bf worker}] {\sc Hisclass} \emp{7, 9, 10, 11 and 12}. \emph{Workers of different skills including farm workers.}
\item[\empr{\bf NA}] {\sc Hisclass} is \empr{missing}.
\end{description}

@@

\begin{frame}{Social class and relative exposure}

\scriptsize
\begin{columns}[t]
\begin{column}{.48\textwidth}
\begin{center}
Social classes

\begin{description}
\item[\bf \textcolor{black}{elite}] {\sc Hisclass} 1 and 2. \emph{Higher managers and professionals.}
\item[\empg{\bf middle}] {\sc Hisclass} \empg{3, 4, 5, 6, and 8}. \emph{Lower managers, lower white collar, and farmers.}
%%\item \emp{\tt lowWhiteC}, HISCLASS 4, 5 and 6. Lower white collar.
\item[\emp{\bf worker}] {\sc Hisclass} \emp{7, 9, 10, 11 and 12}. \emph{Workers of different skills including farm workers.}
\item[\empr{\bf NA}] {\sc Hisclass} is \empr{missing}.
\end{description}

\end{center}
\end{column}
\begin{column}[t]{.48\textwidth}

\includegraphics[height = 3cm]{figs/art2-hiscskumw-1}
\hspace{2cm} Exposure, women

\includegraphics[height = 3cm]{figs/art2-hiscskumm-1}
Exposure, men
\end{column}

\end{columns}

%\begin{frame}{\sc Social class}

%\begin{enumerate}
%\item \emp{\tt elite}, HISCLASS 1 and 2. Higher managers and professionals.
%\item \emp{\tt middle}, HISCLASS 3, 4, 5, 6, and 8. Lower managers, lower white collar, and farmers.
%%\item \emp{\tt lowWhiteC}, HISCLASS 4, 5 and 6. Lower white collar.
%\item \emp{\tt worker}, HISCLASS 7, 9, 10, 11 and 12. Workers of different skills including farm workers.
%\end{enumerate}

@@

\includegraphics[height=5cm]{myfigs/skord05.jpg}
\end{center}

@@

\end{center}

%% Combined slide:
